Subset occurrence data to IUCN Tropical Andes Lowland and Montane Forest

### 2023-08-02 code/L1/L1_TropicalAndes_subset_occ_forest.Rmd
add code to extract values in TropicalAndes_IUCNHabitat_Forest from plant and frugivore occurrence add summary

# Rasterize occurrence data
```{r}
coordinates(TropicalAndes_GBIF_plant_occ_cleaned) <- ~ decimalLatitude + decimalLongitude
coordinates(TropicalAndes_frugivore_occ) <- ~ decimalLatitude + decimalLongitude
# coerce to SpatialPixelsDataFrame
gridded(TropicalAndes_GBIF_plant_occ_cleaned) <- TRUE
gridded(TropicalAndes_frugivore_occ) <- TRUE
# coerce to raster
plant.raster <- raster(TropicalAndes_GBIF_plant_occ_cleaned)
frugivore.raster <- raster(TropicalAndes_frugivore_occ)
```

# Crop occurrence data to forest extent
```{r}
plant_crop <- crop(plants.raster, TropicalAndes_IUCNHabitat_Forest)
plant_occ_forest <- mask(plant_crop, TropicalAndes_IUCNHabitat_Forest)
plot(plant_occ_forest)
plant_occ_forest
```

```{r}
frugivore_crop <- crop(frugivores.raster, TropicalAndes_IUCNHabitat_Forest)
frugivore_occ_forest <- mask(frugivore_crop, TropicalAndes_IUCNHabitat_Forest)
plot(frugivore_occ_forest)
frugivore_occ_forest
```

# Extract species list for plants and frugivore
```{r}
TropicalAndes_plant_Forest_SpeciesList <- unique(TropicalAndes_BIEN_traits$species)
TropicalAndes_frugivore_Forest_SpeciesList <- unique(TropicalAndes_BIEN_traits$species)
```

>>>>

# Rasterize occurrence data
```{r}
# convert to SpatialPointsDataFrame
coordinates(TropicalAndes_GBIF_plant_occ_cleaned) <- ~ decimalLatitude + decimalLongitude
coordinates(TropicalAndes_frugivore_occ) <- ~ decimalLatitude + decimalLongitude
TropicalAndes_GBIF_plant_occ_cleaned
TropicalAndes_frugivore_occ
```

# Crop occurrence data to forest extent
```{r}
TropicalAndes_GBIF_plant_occ_cleaned$ref<- extract(TropicalAndes_IUCNHabitat_Forest, TropicalAndes_GBIF_plant_occ_cleaned)
TropicalAndes_frugivore_occ$ref<- extract(TropicalAndes_IUCNHabitat_Forest, TropicalAndes_frugivore_occ)
```

```{r}
TropicalAndes_GBIF_plant_occ_cleaned$ref <- as.character(TropicalAndes_GBIF_plant_occ_cleaned$ref)
TropicalAndes_frugivore_occ$ref <- as.character(TropicalAndes_frugivore_occ$ref)
```

```{r}
plant_occ_forest <- TropicalAndes_GBIF_plant_occ_cleaned@data
frugivore_occ_forest <- TropicalAndes_frugivore_occ@data
```

```{r}
#remove row if ref = NA
plant_occ_forest <- plant_occ_forest[plant_occ_forest$ref != "NA", ]
frugivore_occ_forest <- frugivore_occ_forest[frugivore_occ_forest$ref != "NA", ]
```

# Summary
```{r}
glimpse(plant_occ_forest)
glimpse(frugivore_occ_forest)
```

```{r}
print("The number of plant records is")
nrow(plant_occ_forest)
print("The number of plant species is")
length(unique(plant_occ_forest$species))
print("The number of plant families is")
length(unique(plant_occ_forest$family))
```

```{r}
print("The number of frugivore records is")
nrow(frugivore_occ_forest)
print("The number of frugivore species is")
length(unique(frugivore_occ_forest$species))
print("The number of frugivore families is")
length(unique(frugivore_occ_forest$family))
```

# Extract species list for plants and frugivore
```{r}
TropicalAndes_plant_Forest_SpeciesList <- unique(plant_occ_forest$species)
TropicalAndes_frugivore_Forest_SpeciesList <- unique(frugivore_occ_forest$species)
```
